Spanner: Google's Globally-Distributed Database \newline Seminar Report

### 2016-02-16 paper/paper.tex
Iterate Schema-Change Transactions

\subsection{Schema-Change Transactions \tbr}
\label{subsec:schema-change-transactions}

Schema-change transactions are variants of standard transactions which change
schemas atomically without blocking the whole system.

There are two phases involved. In the first phase, the \emph{prepare} phase,
Spanner explicitly assigns a future timestamp to the schema-change transaction.
In the phase, reads and writes synchronize with any registered schema-change
timestamp at time $t$. Of course, this concerns only the reads and writes which
implicitly depend on this schema. Any read/write transaction may proceed if
its timestamp preceeds $t$. If its timestamp is after $t$, the corresponding
read/write has to block behind the schema-change transaction. This is essentially
enabled by the TrueTime API because without TrueTime, it would not be guaranteed
that the timestamp of the schema-change transaction is in the future.

>>>>

\subsection{Schema-Change Transactions}
\label{subsec:schema-change-transactions}

Schema-change transactions are variants of standard transactions which change
schemas atomically without blocking any other transactions.

There are two phases involved. In the first phase, the \emph{prepare} phase,
Spanner explicitly assigns a future timestamp to the schema-change transaction.
In the subsequent phase, reads and writes synchronize with any registered
schema-change timestamp at time $t$. Of course, this affects only reads and
writes which implicitly depend on the modified schema. Any read/write transaction
may proceed if its timestamp preceeds $t$. If its timestamp is after $t$, the
corresponding read/write has to block behind the schema-change transaction. This
is essentially enabled by the TrueTime API because without TrueTime, it would
not be guaranteed that the timestamp of the schema-change transaction is in the
future on every single machine.
